---
title: "Estimation of Plant Mating System Parameters: Correlated Paternity at Different Hierarchical Levels"
author: Felipe Torres-Vanegas
date: May 9, 2022
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Selfing Data

## Load Selfing Data

```{r}
data_selfing <- read.csv(paste0(here::here("Output_COLONY/Output_Selfer.txt")))
```

## Identify Selfed Seeds

```{r}
data_selfing <- data_selfing %>% 
  mutate(Selfed = ifelse(Probability >= 0.90, "Yes", "No"))
```

## Identify Maternal Plant ID for each Seed

```{r}
tmp <- Reduce(rbind, strsplit(as.character(data_selfing$OffspringID), split = "_"))

data_selfing <- data_selfing %>% 
  mutate(MomID = tmp[,1])
```

## Identify Bract ID for each Seed

```{r}
data_selfing <- data_selfing %>% 
  mutate(BractID = paste(tmp[,1], tmp[,2], sep = "_"))
```

## Identify Fruit ID for each Seed

```{r}
data_selfing <- data_selfing %>% 
  mutate(FruitID = paste(tmp[,1], tmp[,2], tmp[,3], sep = "_"))
```

## Arrange Column Order

```{r}
data_selfing <- data_selfing %>% 
  select(MomID, OffspringID, BractID, FruitID, Probability, Selfed)
```

# Parentage Assignment Data

## Load Parentage Assignment Data

```{r}
data_paternity <- read.delim(paste0(here::here("Output_COLONY/Output_BestCluster.txt")), header = TRUE, sep = "", dec = ".")
```

# Halfsib Dyads 

## Load Halfsib Dyads 

```{r}
data_halfsibs <- read.csv(paste0(here::here("Output_COLONY/Output_HalfSibDyad.txt")))
```

## Identify Halfsib Dyads

```{r}
data_halfsibs <- data_halfsibs %>% 
  filter(Probability > 0.1)
```

## Complete ID Information for Halfsib Dyads

```{r}
data_halfsibs <- left_join(data_halfsibs,
                           data_selfing %>% 
                             select(MomID, OffspringID, BractID, FruitID, Selfed),
                           by = c("OffspringID1" = "OffspringID"))

data_halfsibs <- left_join(data_halfsibs,
                           data_selfing %>% 
                             select(MomID, OffspringID, BractID, FruitID, Selfed),
                           by = c("OffspringID2" = "OffspringID"))
```

## Rename Columns for Halfsib Dyads

```{r}
data_halfsibs <- data_halfsibs %>% 
  rename(OffspringID1 = OffspringID1,
         OffspringID2 = OffspringID2,
         Probability = Probability,
         MomID1 = MomID.x,
         BractID1 = BractID.x,
         FruitID1 = FruitID.x,
         SelfedID1 = Selfed.x,
         MomID2 = MomID.y,
         BractID2 = BractID.y,
         FruitID2 = FruitID.y,
         SelfedID2 = Selfed.y)
```

## Identify Maternal Halfsib Dyads

```{r}
data_halfsibs <- data_halfsibs %>% 
  mutate(Maternal_Halfsibs = ifelse(MomID1 == MomID2, "Yes", "No"))

data_halfsibs_maternal <- data_halfsibs %>% 
  filter(Maternal_Halfsibs == "Yes") %>% 
  select(-Maternal_Halfsibs)
```

# Fullsib Dyads 

## Load Fullsib Dyads 

```{r}
data_fullsibs <- read.csv(paste0(here::here("Output_COLONY/Output_FullSibDyad.txt")))
```

## Identify Fullsib Dyads

```{r}
data_fullsibs <- data_fullsibs %>% 
  filter(Probability >= 0.9)
```

## Complete ID Information for Fullsib Dyads

```{r}
data_fullsibs <- left_join(data_fullsibs,
                           data_selfing %>% 
                             select(MomID, OffspringID, BractID, FruitID, Selfed),
                           by = c("OffspringID1" = "OffspringID"))

data_fullsibs <- left_join(data_fullsibs,
                           data_selfing %>% 
                             select(MomID, OffspringID, BractID, FruitID, Selfed),
                           by = c("OffspringID2" = "OffspringID"))
```

## Rename Columns for Fullsib Dyads

```{r}
data_fullsibs <- data_fullsibs %>% 
  rename(OffspringID1 = OffspringID1,
         OffspringID2 = OffspringID2,
         Probability = Probability,
         MomID1 = MomID.x,
         BractID1 = BractID.x,
         FruitID1 = FruitID.x,
         SelfedID1 = Selfed.x,
         MomID2 = MomID.y,
         BractID2 = BractID.y,
         FruitID2 = FruitID.y,
         SelfedID2 = Selfed.y)
```

# Maternal Sibships

## Combine Maternal Halfsib Dyads with Fullsib Dyads

```{r}
data_maternal_sibships <- rbind(data.frame(data_halfsibs_maternal, Type = "Maternal_Halfsibs"),
                                data.frame(data_fullsibs, Type = "Fullsibs"))

data_maternal_sibships <- data_maternal_sibships %>% 
  select(-Probability)
```

## Add Patch Information

```{r}
data_maternal_sibships <- data_maternal_sibships %>% 
  mutate(PatchID1 = substr(OffspringID1, 1, 2))

data_maternal_sibships <- data_maternal_sibships %>% 
  mutate(PatchID2 = substr(OffspringID1, 1, 2))
```

## Add Parentage Assignment Data

```{r}
data_maternal_sibships <- left_join(data_maternal_sibships,
                                    data_paternity %>% 
                                       select(OffspringID, FatherID),
                                    by = c("OffspringID1" = "OffspringID"))

data_maternal_sibships <- left_join(data_maternal_sibships,
                                    data_paternity %>% 
                                       select(OffspringID, FatherID),
                                    by = c("OffspringID2" = "OffspringID"))
```

## Rename Columns

```{r}
data_maternal_sibships <- data_maternal_sibships %>% 
  rename(DadID1 = FatherID.x,
         DadID2 = FatherID.y)
```

## Removed Selfed Seeds

```{r}
data_maternal_sibships_outcrossed <- data_maternal_sibships %>% 
  filter(SelfedID1 == "No",
         SelfedID2 == "No")
```

## Arrange Column Order

```{r}
data_maternal_sibships <- data_maternal_sibships %>% 
  select(OffspringID1, OffspringID2, PatchID1, PatchID2, MomID1, MomID2, BractID1, BractID2, FruitID1, FruitID2, SelfedID1, SelfedID2, DadID1, DadID2, Type)

data_maternal_sibships_outcrossed <- data_maternal_sibships_outcrossed %>% 
  select(OffspringID1, OffspringID2, PatchID1, PatchID2, MomID1, MomID2, BractID1, BractID2, FruitID1, FruitID2, SelfedID1, SelfedID2, DadID1, DadID2, Type)
```

# Paternal Halfsib Dyads

## Load Paternal Halfsib Dyads Data

```{r}
data_halfsibs_paternal <- read.csv(paste0(here::here("Output_COLONY/Output_Seed_Pairs_Among_Moms.txt")))
```

## Include Patch Information

```{r}
data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  mutate(PatchID1 = substr(OffspringID1, 1, 2))

data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  mutate(PatchID2 = substr(OffspringID2, 1, 2))
```

## Restrict Seed Pairs to Within Sampling Location

```{r}
data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  filter(PatchID1 == PatchID2)
```

## Add Selfing Information

```{r}
data_halfsibs_paternal <- left_join(data_halfsibs_paternal,
                                    data_selfing %>% 
                                      select(MomID, OffspringID, BractID, FruitID, Selfed),
                                    by = c("OffspringID1" = "OffspringID"))

data_halfsibs_paternal <- left_join(data_halfsibs_paternal,
                                    data_selfing %>% 
                                      select(MomID, OffspringID, BractID, FruitID, Selfed),
                                    by = c("OffspringID2" = "OffspringID"))
```

## Add Parentage Assignment Data

```{r}
data_halfsibs_paternal <- left_join(data_halfsibs_paternal,
                                    data_paternity %>% 
                                      select(OffspringID, FatherID),
                                    by = c("OffspringID1" = "OffspringID"))

data_halfsibs_paternal <- left_join(data_halfsibs_paternal,
                                    data_paternity %>% 
                                      select(OffspringID, FatherID),
                                    by = c("OffspringID2" = "OffspringID"))
```

## Rename Columns

```{r}
data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  rename(OffspringID1 = OffspringID1,
         OffspringID2 = OffspringID2,
         PatchID1 = PatchID1,
         PatchID2 = PatchID2,
         MomID1 = MomID.x,
         BractID1 = BractID.x,
         FruitID1 = FruitID.x,
         SelfedID1 = Selfed.x,
         MomID2 = MomID.y,
         BractID2 = BractID.y,
         FruitID2 = FruitID.y,
         SelfedID2 = Selfed.y,
         DadID1 = FatherID.x,
         DadID2 = FatherID.y)
```

## Remove Seeds with Known Father from the Same Sampling Location (Near-Neighbor Mating)

```{r}
data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  filter(str_detect(DadID1, "#"))

data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  filter(str_detect(DadID2, "#"))
```

## Remove Selfed Seeds

```{r}
data_halfsibs_paternal_outcrossed <- data_halfsibs_paternal %>% 
  filter(SelfedID1 == "No",
         SelfedID2 == "No")
```

## Add Sibship Type

```{r}
data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  mutate(Type = ifelse(DadID1 == DadID2, "Paternal_Halfsibs", "Nonsibs"))

data_halfsibs_paternal_outcrossed <- data_halfsibs_paternal_outcrossed %>% 
  mutate(Type = ifelse(DadID1 == DadID2, "Paternal_Halfsibs", "Nonsibs"))
```

## Arrange Column Order

```{r}
data_halfsibs_paternal <- data_halfsibs_paternal %>% 
  select(OffspringID1, OffspringID2, PatchID1, PatchID2, MomID1, MomID2, BractID1, BractID2, FruitID1, FruitID2, SelfedID1, SelfedID2, DadID1, DadID2, Type)

data_halfsibs_paternal_outcrossed <- data_halfsibs_paternal_outcrossed %>% 
  select(OffspringID1, OffspringID2, PatchID1, PatchID2, MomID1, MomID2, BractID1, BractID2, FruitID1, FruitID2, SelfedID1, SelfedID2, DadID1, DadID2, Type)
```

# Assemble Sibship Data

```{r}
data_dyads <- rbind(data_maternal_sibships, data_halfsibs_paternal)

data_dyads_outcrossed <- rbind(data_maternal_sibships_outcrossed, data_halfsibs_paternal_outcrossed)
```

# Load FPR and FNR Error Rates

```{r}
error_rates <- readRDS(paste0(here::here("Output_COLONY/FPR_FNR_Error_Rates.rds")))
```

# Function to Correct Plant Mating System Parameters for FPR and FNR Error Rates

```{r}
corrected_mating_estimates <- function(T, N, SE_Initial, SP, SE_Correct)
{
  P <- T / N
  
  Estimate <- (P - (1 - SP)) / (SE_Correct + SP - 1)
  SE_Corrected <- as.numeric(SE_Initial / (SE_Correct + SP - 1))
  
  data.frame(Observed_Estimate = P,
             SE_Initial = SE_Initial,
             Corrected_Estimate = Estimate,
             SE_Corrected = SE_Corrected,
             Observed = T,
             Inferred = Estimate * N)
}
```

# Estimate Mean Correlated Paternity at Different Hierarchical Levels

```{r}
corr_pat <- function(df)
{
  corr_pat_within_moms <- 
    nrow(df %>% filter(Type == "Fullsibs")) /
    nrow(df %>% filter(Type %in% c("Fullsibs", "Maternal_Halfsibs")))
  
  corr_pat_within_fruits <-
    nrow(df %>% filter(FruitID1 == FruitID2, Type == "Fullsibs")) /
    nrow(df %>% filter(FruitID1 == FruitID2, Type %in% c("Fullsibs", "Maternal_Halfsibs")))
  
  corr_pat_among_fruits <-
    nrow(df %>% filter(FruitID1 != FruitID2, Type == "Fullsibs")) /
    nrow(df %>% filter(FruitID1 != FruitID2, Type %in% c("Fullsibs", "Maternal_Halfsibs")))
  
  corr_pat_among_fruits_same_bract <-
    nrow(df %>% filter(FruitID1 != FruitID2, BractID1 == BractID2, Type == "Fullsibs")) /
    nrow(df %>% filter(FruitID1 != FruitID2, BractID1 == BractID2, Type %in% c("Fullsibs", "Maternal_Halfsibs")))
  
  corr_pat_among_moms <- 
    nrow(df %>% filter(Type == "Paternal_Halfsibs")) /
    nrow(df %>% filter(Type %in% c("Paternal_Halfsibs", "Nonsibs")))
  
  return(c(corr_pat_within_moms, corr_pat_within_fruits, corr_pat_among_fruits, corr_pat_among_fruits_same_bract, corr_pat_among_moms))
}
```

```{r}
boot_corr_pat <- function(dataframe, indices)
{
  d <- dataframe[indices,]
  return(as.numeric(corr_pat(d)))
}
```

```{r}
corr_pat <- boot(data_dyads,
                 boot_corr_pat,
                 R = 1000)
```

```{r}
corr_pat_outcrossed <- boot(data_dyads_outcrossed,
                            boot_corr_pat,
                            R = 1000)
```

## Estimate Mean Correlated Paternity Within Maternal Plants: Correct for FPR and FNR Error Rates

```{r}
cor_pat_within_moms_corrected <- function(df)
{
  cor_pat_within_moms <- corrected_mating_estimates(T = nrow(df %>% 
                                                               filter(Type == "Fullsibs")),
                                             N = nrow(df %>% 
                                                        filter(Type %in% c("Fullsibs", "Maternal_Halfsibs"))),
                                             SE_Initial = 0.0054697125,
                                             SP = 1 - error_rates$Full_Sibs_FPR,
                                             SE_Correct = 1 - error_rates$Full_Sibs_FNR)
  
  return((cor_pat_within_moms))
}

cor_pat_within_moms <- cor_pat_within_moms_corrected(data_dyads_outcrossed)
```

## Estimate Mean Correlated Paternity Within Fruits: Correct for FPR and FNR Error Rates

```{r}
cor_pat_within_fruits_corrected <- function(df)
{
  cor_pat_within_fruits <- corrected_mating_estimates(T = nrow(df %>% 
                                                                           filter(FruitID1 == FruitID2, Type == "Fullsibs")),
                                             N = nrow(df %>% 
                                                        filter(FruitID1 == FruitID2, Type %in% c("Fullsibs", "Maternal_Halfsibs"))),
                                             SE_Initial = 0.0190657382,
                                             SP = 1 - error_rates$Full_Sibs_FPR,
                                             SE_Correct = 1 - error_rates$Full_Sibs_FNR)
  
  return((cor_pat_within_fruits))
}

cor_pat_within_fruits <- cor_pat_within_fruits_corrected(data_dyads_outcrossed)
```

## Estimate Mean Correlated Paternity Among Fruits Same Bract: Correct for FPR and FNR Error Rates

```{r}
cor_pat_among_fruits_corrected <- function(df)
{
  cor_pat_among_fruits <- corrected_mating_estimates(T = nrow(df %>% 
                                                                filter(FruitID1 != FruitID2,
                                                                       BractID1 == BractID2,
                                                                       Type == "Fullsibs")),
                                             N = nrow(df %>% 
                                                        filter(FruitID1 != FruitID2,
                                                               BractID1 == BractID2,
                                                               Type %in% c("Fullsibs", "Maternal_Halfsibs"))),
                                             SE_Initial = 0.0071995857,
                                             SP = 1 - error_rates$Full_Sibs_FPR,
                                             SE_Correct = 1 - error_rates$Full_Sibs_FNR)
  
  return((cor_pat_among_fruits))
}

cor_pat_among_fruits <- cor_pat_among_fruits_corrected(data_dyads_outcrossed)
```

## Estimate Mean Correlated Paternity Among Maternal Plant Same Sampling Location: Correct for FPR and FNR Error Rates

```{r}
cor_pat_among_moms_corrected <- function(df)
{
  cor_pat_among_moms <- corrected_mating_estimates(T = nrow(df %>%
                                                              filter(Type == "Paternal_Halfsibs")),
                                             N = nrow(df %>% 
                                                        filter(Type %in% c("Paternal_Halfsibs", "Nonsibs"))),
                                             SE_Initial = 0.0007672469,
                                             SP = 1 - error_rates$Paternal_Half_Sibs_FPR,
                                             SE_Correct = 1 - error_rates$Paternal_Half_Sibs_FNR)
  
  return((cor_pat_among_moms))
}

cor_pat_among_moms <- cor_pat_among_moms_corrected(data_dyads_outcrossed)
```

# Assemble Estimates of Correlated Paternity

```{r}
correlated_paternity_estimates <- data.frame(Level = c("Wihtin_Moms",
                                                       "Within_Fruits",
                                                       "Among_Fruits",
                                                       "Among_Moms"),
                                             Observed = c(cor_pat_within_moms$Observed,
                                                          cor_pat_within_fruits$Observed,
                                                          cor_pat_among_fruits$Observed,
                                                          cor_pat_among_moms$Observed),
                                             Observed_Estimate = c(cor_pat_within_moms$Observed_Estimate,
                                                                   cor_pat_within_fruits$Observed_Estimate,
                                                                   cor_pat_among_fruits$Observed_Estimate,
                                                                   cor_pat_among_moms$Observed_Estimate),
                                             Observed_SE = c(cor_pat_within_moms$SE_Initial,
                                                             cor_pat_within_fruits$SE_Initial,
                                                             cor_pat_among_fruits$SE_Initial,
                                                             cor_pat_among_moms$SE_Initial),
                                             Corrected_Estimate = c(cor_pat_within_moms$Corrected_Estimate,
                                                                    cor_pat_within_fruits$Corrected_Estimate,
                                                                    cor_pat_among_fruits$Corrected_Estimate,
                                                                    cor_pat_among_moms$Corrected_Estimate),
                                             Corected_SE = c(cor_pat_within_moms$SE_Corrected,
                                                             cor_pat_within_fruits$SE_Corrected,
                                                             cor_pat_among_fruits$SE_Corrected,
                                                             cor_pat_among_moms$SE_Corrected))

correlated_paternity_estimates
```