---
title: "Estimation of Plant Mating System Parameters: Type of Mating Events"
author: Felipe Torres-Vanegas
date: May 9, 2022
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Selfing Data

## Load Selfing Data

```{r}
data_selfing <- read.csv(paste0(here::here("Output_COLONY/Output_Selfer.txt")))
```

## Identify Selfed Seeds

```{r}
data_selfing <- data_selfing %>% 
  mutate(Selfed = ifelse(Probability >= 0.90, "Yes", "No"))
```

## Remove Seed with Ambiguous Parentage Assignment

```{r}
data_selfing <- data_selfing %>% 
  filter(OffspringID != "29E_B5_F4_10_2016")
```

# Parent Pair Data

## Load Parent Pair Data

```{r}
data_parent_pair <- read.csv(paste0(here::here("Output_COLONY/Output_ParentPair.txt")))
```

## Select Seeds with Probability >= 0.90

```{r}
data_parent_pair <- data_parent_pair %>% 
  filter(Probability >= 0.90)
```

## Add Forest Patch ID

```{r}
data_parent_pair <- data_parent_pair %>% 
  mutate(DadPatch = substr(InferredDad, 1, 2))

data_parent_pair <- data_parent_pair %>% 
  mutate(MumPatch = substr(InferredMum, 1, 2))
```

## Select Outcrossed Seeds

```{r}
data_parent_pair <- left_join(data_parent_pair,
                              data_selfing %>% 
                                dplyr::select(OffspringID, Selfed),
                              by = c("OffspringID" = "OffspringID"))

data_parent_pair_outcrossed <- data_parent_pair %>% 
  filter(Selfed == "No")
```

# Identify Near-Neighbor Mating Events

```{r}
near_mating <- data_parent_pair %>% 
  filter(DadPatch == MumPatch) %>% 
  filter(as.character(InferredDad) != as.character(InferredMum))
```

# Load FPR and FNR Error Rates

```{r}
error_rates <- readRDS(paste0(here::here("Output_COLONY/FPR_FNR_Error_Rates.rds")))
```

# Function to Correct Plant Mating System Parameters for FPR and FNR Error Rates

```{r}
corrected_mating_estimates <- function(T, N, SE_Initial, SP, SE_Correct)
{
  P <- T / N
  
  Estimate <- (P - (1 - SP)) / (SE_Correct + SP - 1)
  SE_Corrected <- as.numeric(SE_Initial / (SE_Correct + SP - 1))
  
  data.frame(Observed_Estimate = P,
             SE_Initial = SE_Initial,
             Corrected_Estimate = Estimate,
             SE_Corrected = SE_Corrected,
             Observed = T,
             Inferred = Estimate * N)
}
```

# Estimate Rate of Selfing and Outcrossing

```{r}
rate_selfing_outcrossing <- function(df)
{
  rate_selfing <- nrow(df %>% 
                         filter(Selfed == "Yes")) / nrow(df)
  
  rate_outcrossing <- nrow(df %>% 
                             filter(Selfed == "No")) / nrow(df)
  
  return(c(rate_selfing, rate_outcrossing))
}
```

```{r}
boot_rate_selfing_outcrossing <- function(dataframe, indices)
{
  d <- dataframe[indices,]
  return(as.numeric(rate_selfing_outcrossing(d)))
}
```

```{r}
rate_selfing_outcrossing <- boot(data_selfing,
                                 boot_rate_selfing_outcrossing,
                                 R = 1000)
```

## Estimate Rate of Selfing: Correct for FPR and FNR Error Rates

```{r}
rate_selfing_corrected <- function(df)
{
  rate_selfing <- corrected_mating_estimates(T = nrow(df %>% 
                                                        filter(Selfed == "Yes")),
                                             N = nrow(df),
                                             SE_Initial = 0.005518234,
                                             SP = 1 - error_rates$Selfing_FPR,
                                             SE_Correct = 1 - error_rates$Selfing_FNR)
  
  return((rate_selfing))
}

rate_selfing <- rate_selfing_corrected(data_selfing)
```

## Estimate Rate of Outcrossing: Correct for FPR and FNR Error Rates

```{r}
rate_outcrossing_corrected <- function(df)
{
  rate_outcrossing <- corrected_mating_estimates(T = nrow(df %>% 
                                                            filter(Selfed == "No")),
                                                 N = nrow(df),
                                                 SE_Initial = 0.005518234,
                                                 SP = 1 - error_rates$Selfing_FPR,
                                                 SE_Correct = 1 - error_rates$Selfing_FNR)
  
  return((rate_outcrossing))
}

rate_outcrossing <- rate_outcrossing_corrected(data_selfing)
```

# Estimate Rate of Near-Neighbor and Non-Near-Neighbor Mating

```{r}
rate_near_non_near_mating <- function(df)
{
  rate_near <- nrow(df %>% 
                      filter(DadPatch == MumPatch) %>% 
                      filter(as.character(InferredDad) != as.character(InferredMum))) / nrow(df)
  
  rate_non_near <- nrow(df %>% 
                          filter(DadPatch != MumPatch) %>% 
                          filter(as.character(InferredDad) != as.character(InferredMum))) / nrow(df)
  
  return(c(rate_near, rate_non_near))
}
```

```{r}
boot_rate_near_non_near_mating <- function(dataframe, indices)
{
  d <- dataframe[indices,]
  return(as.numeric(rate_near_non_near_mating(d)))
}
```

```{r}
rate_near_non_near_mating <- boot(data_parent_pair,
                                  boot_rate_near_non_near_mating,
                                  R = 1000)
```

## Estimate Rate of Near-Neighbor Mating: Correct for FPR and FNR Error Rates

```{r}
rate_near_mating_corrected <- function(df)
{
  rate_near <- corrected_mating_estimates(T = nrow(near_mating),
                                          N = nrow(data_parent_pair),
                                          SE_Initial = 0.003781389,
                                          SP = 1 - error_rates$Near_Mating_FPR,
                                          SE_Correct = 1 - error_rates$Near_Mating_FNR)
  
  return((rate_near))
}

rate_near <- rate_near_mating_corrected(data_parent_pair)
```

## Estimate Rate of Non-Near-Neighbor Mating: Correct for FPR and FNR Error Rates

```{r}
rate_non_near_mating_corrected <- function(df)
{
  rate_non_near <- corrected_mating_estimates(T = nrow(data_parent_pair) - nrow(near_mating) - nrow(data_selfing %>%
                                                                                                      filter(Selfed == "Yes")),
                                              N = nrow(data_parent_pair),
                                              SE_Initial = 0.006741935,
                                              SP = NA,
                                              SE_Correct = NA)
  
  return((rate_non_near))
}

rate_non_near <- rate_non_near_mating_corrected(data_parent_pair)
```

# Assemble Type of Mating Events

```{r}
type_mating_events <- data.frame(Mating_Type = c("Selfing",
                                                 "Near-Neighbour",
                                                 "Non-Near-Neighbour",
                                                 "Outcrossing"),
                                 Observed = c(rate_selfing$Observed,
                                              rate_near$Observed,
                                              rate_non_near$Observed,
                                              rate_outcrossing$Observed),
                                 Observed_Estimate = c(rate_selfing$Observed_Estimate,
                                                       rate_near$Observed_Estimate,
                                                       rate_non_near$Observed_Estimate,
                                                       rate_outcrossing$Observed_Estimate),
                                 Observed_SE = c(rate_selfing$SE_Initial,
                                                 rate_near$SE_Initial,
                                                 rate_non_near$SE_Initial,
                                                 rate_outcrossing$SE_Initial),
                                 Corrected_Estimate = c(rate_selfing$Corrected_Estimate,
                                                        rate_near$Corrected_Estimate,
                                                        1 - rate_selfing$Corrected_Estimate - rate_near$Corrected_Estimate,
                                                        rate_outcrossing$Corrected_Estimate),
                                 Corected_SE = c(rate_selfing$SE_Corrected,
                                                 rate_near$SE_Corrected,
                                                 rate_non_near$SE_Initial,
                                                 rate_outcrossing$SE_Corrected))

type_mating_events
```