---
title: "Simulation Modeling of Pollen Loads, Inference of Pollinator Foraging Tactics, and Sensitivity Analysis"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
---

## 1. Preparations

Load packages, import data, and define functions used for simulating pollen loads and calculating expected values of mating system parameters from them.

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

### Load packages

```{r include=FALSE}
library(ggplot2)
library(tidyverse)
library(tidyr)
library(dplyr)
#library(parallel)
#library(pbmcapply)
```

### Import observed mating system parameters

Import observed mating system parameters (corrected for false positive/negative rates). 

- Corrected_Rate: observed rates, corrected for FPR/FNR determined from simulation without genotyping error. Not used here.
- Corrected_Rate_Mismatches: observed rates, corrected for FPR/FNR determined from simulation with genotyping error. These were used here. 
- Uncorrected: uncorrected observed rates. Not used here.

```{r}
Rates.table <- readRDS(paste0(here::here(), "/parameters_new_errors.rds")) #"/FPR_FNR_Error_Rates.rds"
row.names(Rates.table) <- Rates.table$Paremeter
Rates.table <- Rates.table[,-1]

Rates.table$Uncorrected <- c(0.02583026, 0.01262626, 0.2136364, 0.1296044, 0.008493686)

Rates.table
```

### Create list of lists to compile results

```{r}
Fitted <- list(p.fit = data.frame(matrix(NA, nrow=ncol(Rates.table),ncol=4, 
                       dimnames=list(names(Rates.table), c("fit", "min", "max", "SE")))),
                    p.SST = list(),
                    p = list(),
                    p.RMV = list(),
                    N.NBR = list(),
                    Set = list(),
                    Smoothing = list(),
                    Scenarios = list(),
                    Sensitivity.Table = list(),
                    Set.Table = list(),
                    Bias = list(),
                    p.TF = list(),
                    p2 = list(),
                    nTotal = list())

#Fitted <- readRDS(paste0(here::here(), "/Fitted.rds"))
```

### Function `get.p.fit.within`

Function to estimate the parameter p of the geometric distribution assuming complete traplining (`p.SST = 0`).

- Est: estimate of CP.within.fruit.
- n: number of pollen donors for which to calculate probability to include in sum.
- Function calculated the expected CP for a range of parameter values of p and identifies the value that results in CP closest to the observed rate.

```{r}
get.p.fit.within <- function(Est=0.2089927, n = 100)
{
  p <- 1/seq(2,4,0.001)
  CP <- sapply(p, function(x) sum(dgeom(c(1:n)-1, x)^2))

  p.fit.within <- p[which(abs(CP - Est) == min(abs(CP - Est)))]
  p.fit.within
}
```

### Function `get.donorlist`

Function to simulate pollen loads:

```{r}
get.donorlist <- function(p.SST=0, N.NBR=5, p.RMV=1, nFruit=135, p=1/3, 
                          p.TF=0, p2=1/2, nTotal=120, nSites=100)
{
  # Version date: Feb 18, 2022
  if(p.TF > 0 & p.SST > 0) cat("Please set p.TF or p.SST to 0!")
    
  Routes <- list()
  for(m in 1:N.NBR) Routes[[m]] =  paste(LETTERS[m], c(1:nSites), sep=".")
  names(Routes) <- LETTERS[1:N.NBR]
  
  Clusters <- list()
  for(m in 1:round(nTotal/N.NBR)) Clusters[[m]] = paste("L",m, c(1:N.NBR), sep=".")
  Clusters[[1]] <- paste(LETTERS[1:N.NBR], 0, sep=".")
  
  # Create exhaustive list of pollen donors, same list for each mom
  tmp <- unlist(Routes)
  tmp.2 <- unlist(Clusters[-1])
  DonorList <- data.frame(PollenDonors = c(paste(names(Routes), 0, sep="."), tmp,
                          as.vector(outer(paste0(tmp, "_"), c(2:N.NBR), paste0)),
                          unlist(Clusters[-1]))) # NEW
  rownames(DonorList) <- DonorList$PollenDonors
  DonorList <- rep(list(DonorList), N.NBR) 

  # Here, fruit = day: fruits of the same day are correlated if TF
  # i.e., the same bird visits the N.NBR plants in random order
  
  for(f in 1:nFruit)
  { 
    # Is today's bird a territorial forager?
    is.TF = FALSE
    if(p.TF > 0 & runif(1) < p.TF) 
    {
      is.TF = TRUE
      a.TF = sample(N.NBR)
      PollenDonors.TF <- lapply(Clusters, sample)
      PollenDonors.TF <- PollenDonors.TF[c(1, sample(2:length(Clusters)))]
    }
    
    for(m in 1:N.NBR)  
    {
      tmp1 <- c()
      j.start = 1
      
      # Territorial foraging module:
      # ---------------------------
      if(is.TF == TRUE)
      {
        PollenDonors <- PollenDonors.TF
        PollenDonors[[1]] <- Clusters[[1]][a.TF[cumsum(a.TF==m)<1]]
        PollenDonors <- unlist(PollenDonors)
      }
      
      # Trapling foraging module:
      # ------------------------
      if(is.TF == FALSE) 
      {
        # Select which route will be sampled:
        # ----------------------------------
        # With probability (1-p.shift), this will be route m.
        # With probability of p.shift, this will be a randomly chosen route (other than m)
        # All other routes have the same probability
        # It is assumed that 'sampling' before 'shifting' does not result in pollination
        # and that the pollinator only shifts once per day and resource location.
        # Hence, no correlated pollinations on the same day (different from TF). 
        
        # Random shifting according to p.SST and N.NBR:
        Steps <- sample(1:N.NBR, 1, prob=c(rep(p.SST/(N.NBR-1), N.NBR-1), 1-p.SST))
        a <- c(1:N.NBR, 1:N.NBR)[Steps + c(1:N.NBR)]
  
        # Complete trapline foraging sub-module:
        # -------------------------------------
        PollenDonors <- Routes[[a[m]]]
        
        # Sample-and-shift foraging sub-module:
        # ------------------------------------
        # This will modify the list of pollen donors from the 
        # complete trapline foraging sub-module
        
        if(p.SST > 0 & Steps != N.NBR) 
        {
          tmp1 = paste(names(Routes)[a[m]], 0,sep=".")
          PollenDonors <- c(tmp1, PollenDonors)
          j.start = 2
        }  
        
        # Simulate sample-and-shift at previously visited sampling locations  
        Add <- c()
        for(j in j.start:length(PollenDonors))
        {
          if(runif(1) < p.SST) 
          {
            new = paste(PollenDonors[j], sample(c(2:N.NBR),1), sep="_")
            if(N.NBR == 2) new = paste(PollenDonors[j], 2, sep="_")
            Add = c(Add, new)
          }
        }
        
        if(length(Add) > 0)
        {
          PollenDonors <- c(PollenDonors, Add)
          tmp <- split(PollenDonors, sapply(strsplit(PollenDonors, split="_"), 
                                            function(x) x[[1]][1]))
          tmp <- tmp[order(as.numeric(sapply(strsplit(names(tmp), split="[.]"), 
                                             function(x) x[[2]])))]
          PollenDonors <- as.character(unlist(sapply(tmp, 
                                       function(x) sort(x, decreasing=TRUE))))
          tmp1 <- c(tmp1, sapply(strsplit(Add, split="_"), function(x) x[[1]][1]))
        }
  
      }
      
      # For all foraging types:
      # ----------------------
      # Determine probability of each pollen donor to sire seed.
      # For SST, reduce probabilities for sampled plants according to p.RMV:
      
      if(is.TF==TRUE) 
      {
        Prob <- p2
        for(d in 2:length(PollenDonors)) Prob[d] = p2 * (1-sum(Prob)) 
      }
      
      if(is.TF==FALSE) 
      {
        b <- !is.element(PollenDonors, tmp1)
        Prob <- p
        if(j.start==2) Prob = p * p.RMV 
        for(d in 2:length(PollenDonors)) Prob[d] = p * (1-sum(Prob)) * c(p.RMV, 1)[b[d]+1]
      }
      
      # Add column of pollen donor probabilities for fruit f of plant m to DonorList:
      tmp <- data.frame(PollenDonors, Prob)
      names(tmp)[2] <- paste0("F",f)
      DonorList[[m]] <- left_join(DonorList[[m]], tmp, 
                                  by=c("PollenDonors" ="PollenDonors"))
    }
  }
  
  # Tidy up DonorList:
  # -----------------
  for(m in 1:N.NBR)
  {
    rownames(DonorList[[m]]) <- DonorList[[m]]$PollenDonors
    DonorList[[m]] <- DonorList[[m]][,-1]
    DonorList[[m]][is.na(DonorList[[m]])] <- 0
    colSums(DonorList[[m]])
  }
  names(DonorList) <- names(Routes)
  DonorList
}
```

### Function `get.CP`

Function to extract mating system parameters from simulated pollen distributions. 

```{r}
get.CP <- function(DonorList)
{
  # Version date: Feb 18, 2022
  
  N.NBR=length(DonorList)
  CP.res <- data.frame(matrix(NA, 2, 6, dimnames=list(c("All", "Sample"), 
                c("CP.within.fruit", "CP.between.fruit", "CP.within.mom", 
                  "CP.between.mom", "Local", "Nep"))))
  
  # Calculate expected rates based on probabilities
  
  res <- data.frame(matrix(NA, N.NBR, 3, dimnames=list(names(DonorList), 
                    c("CP.within.fruit", "CP.between.fruit", "Local"))))
  for(m in 1:length(DonorList))
  {
    tmp <- t(data.matrix(DonorList[[m]])) %*% data.matrix(DonorList[[m]])
    CP.within.fruit <- mean(diag(tmp))
    CP.between.fruit <- mean(tmp[lower.tri(tmp)])
    Local <- mean(colSums(DonorList[[m]][1:N.NBR,]))
    res[m,] <- c(CP.within.fruit, CP.between.fruit, Local)
  }

  CP.res["All", "CP.within.fruit"] <- mean(res$CP.within.fruit)
  CP.res["All", "CP.between.fruit"] <- mean(res$CP.between.fruit)
  CP.res["All", "Local"] <- mean(res$Local)
  
  tmp <-sapply(DonorList, function(ls) apply(ls, 1, mean))
  
  tmp <- t(tmp) %*% tmp
  CP.res["All", "CP.within.mom"] <- mean(diag(tmp))
  CP.res["All", "CP.between.mom"] <- mean(tmp[lower.tri(tmp)])
  CP.res["All", "Nep"] <- 1/CP.res["All", "CP.within.mom"]
  
  CP.res
}
```

```{r}
get.CP.site <- function(DonorList)
{
  # Version date: April 12, 2022
  
  N.NBR=length(DonorList)
  CP.res <- data.frame(matrix(NA, 2, 8, dimnames=list(c("All", "Sample"), 
                c("CP.within.fruit", "CP.between.fruit", "CP.within.mom", 
                  "CP.between.mom", "Local", "Nep", "CP.within.site", "Nep.site"))))
  
  # Calculate expected rates based on probabilities
  
  res <- data.frame(matrix(NA, N.NBR, 3, dimnames=list(names(DonorList), 
                    c("CP.within.fruit", "CP.between.fruit", "Local"))))
  for(m in 1:length(DonorList))
  {
    tmp <- t(data.matrix(DonorList[[m]])) %*% data.matrix(DonorList[[m]])
    CP.within.fruit <- mean(diag(tmp))
    CP.between.fruit <- mean(tmp[lower.tri(tmp)])
    Local <- mean(colSums(DonorList[[m]][1:N.NBR,]))
    res[m,] <- c(CP.within.fruit, CP.between.fruit, Local)
  }

  CP.res["All", "CP.within.fruit"] <- mean(res$CP.within.fruit)
  CP.res["All", "CP.between.fruit"] <- mean(res$CP.between.fruit)
  CP.res["All", "Local"] <- mean(res$Local)
  
  tmp <-sapply(DonorList, function(ls) apply(ls, 1, mean))
  
  # NEW April 2022: Nep.site
  tmp2 <- apply(tmp, 1, mean)
  #CP.within.site <- t(tmp2) %*% tmp2
  #Nep.site <- 1/CP.within.site
  #c(CP.within.site, Nep.site)
  CP.res["All", "CP.within.site"] <- t(tmp2) %*% tmp2
  CP.res["All", "Nep.site"] <- 1/CP.res["All", "CP.within.site"]
  
  tmp <- t(tmp) %*% tmp
  CP.res["All", "CP.within.mom"] <- mean(diag(tmp))
  CP.res["All", "CP.between.mom"] <- mean(tmp[lower.tri(tmp)])
  CP.res["All", "Nep"] <- 1/CP.res["All", "CP.within.mom"]
  #1/mean(diag(tmp))
  
  CP.res
} 
```

### Wrapper function `fx`

This function:

- Simulates pollen distributions (pollen loads).
- Calculates CP values.

```{r}
fx <- function(y=0, z=0, w=5, nFruit=135, nSites=100,
               u=0, v=Fitted$p.fit[r,1], t=120, p=Fitted$p.fit[r,1]) 
{
  # Version date: April 1, 2021
  
  D <- get.donorlist(p.SST=y, p.RMV=z, N.NBR=w, nFruit=nFruit, p=p,
                     p.TF=u, p2=v, nTotal=t)
  CP <- get.CP(D)
  unlist(CP["All",])
}
```

## 2. Pattern-oriented simulation modeling for complete vs. sample-and-shift traplining

### Step 1: Expressing p.RMV as a function of p and p.SST

#### Special case: complete traplining

Under complete traplining, p.SST = 0, and p.RMV is irrelevant as no plants are "sampled". Thus, p can be estimated directly from the observed correlated paternity within fruits (assuming that each fruit results from pollination by a single pollinator visit).

Here we apply the function `get.p.fit.within` to get estimate of p ± SE for complete traplining.

```{r}
Fitted$p.fit <- data.frame(matrix(NA, ncol(Rates.table), 3,
                           dimnames=list(names(Rates.table), c("fit", "min", "max"))))
for(r in 1:ncol(Rates.table))
{
  # Version date: 9 March 2021
  
  Estimate = Rates.table["Within Fruit Outcrossed", r]
  SE = SE.table["Within Fruit Outcrossed", r]

  Fitted$p.fit[r,1:3] <- c(fit = get.p.fit.within(Est=Estimate, n = 100),
                        min = get.p.fit.within(Est=Estimate - SE, n = 100),
                        max = get.p.fit.within(Est=Estimate + SE, n = 100))
  Fitted$p.fit[r,"SE"] <- (Fitted$p.fit[r,"max"]  - Fitted$p.fit[r,"min"] )/2
}

Fitted$p.fit
```

#### Model the rate of local pollination

Relationship between `p`, `p.SST` and `p.RMV` to express `p.RMV` as a function of `p` and `p.SST`: `p.RMV = Estimate / (p * p.SST)`.

```{r}
r = 2  # Select set of observed rates

Estimate <- Rates.table["Local Mating Outcrossed", r]

P.RMV.opt <- expand.grid(p=seq(0.25,0.5,0.05), 
                             p.SST=sort(c(seq(0.05,0.3,0.05), c(0.125, 0.175))))
P.RMV.opt <- P.RMV.opt %>% 
  mutate(p.RMV=Estimate / ( p * p.SST)) %>%
  mutate(p.RMV = replace(p.RMV, p.RMV > 1, NA)) %>%
  filter(!is.na(p.RMV))

Fitted$p.RMV[[r]] <- P.RMV.opt
```

### Step 2: Expressing p as a function of p.SST

#### Model CP within fruit 

Model CP within fruit as a function of `p`, `p.SST` and `p.RMV` to express `p` as a function of `p.SST` (and the associated value of `p.RMV`).

```{r}
X <- Fitted$p.RMV[[r]]
R <- 30
X <- X[rep(1:nrow(X),R),]
Res <- data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                       fx(y=X$p.SST[i], z=X$p.RMV[i], w=10, p=X$p[i]), 
                          mc.cores=parallel::detectCores())))

Res.p <- Res
saveRDS(Res.p, paste0(here::here(), "/Res.p.rds"))
#Res.p <- readRDS(paste0(here::here(), "/Res.p.rds"))

Estimate <- Rates.table["Within Fruit Outcrossed", r]
```

Optimization: `p.opt` as a function of `p.SST`

```{r}
optimize.p <- function(x, E, a, b1, b2)
{
  (E - (a + b1 * x + b2 * I(x^2)))^2
}

get.p <- function(ls)
{
  # Version date: April 8, 2021
  
  mod1 <- lm(CP.within.fruit ~ p + p.2, 
                       data=ls %>% mutate(p.2 = p^2))
  p.opt <- NA
  if(sum(is.na(mod1$coef)) == 0)
  {
    p.opt <- optimize(optimize.p, interval=c(0.25, 0.5), 
                    E=Estimate, a=mod1$coef[1], b1=mod1$coef[2], b2=mod1$coef[3])$minimum
  }
  
  c(a=mod1$coef[1], b1=mod1$coef[2], b2=mod3$coef[3], p.opt=p.opt)
}

Res.p <- Res.p %>% mutate(p.SST.f = factor(p.SST))

test <- split(Res.p, Res.p$p.SST.f)  # Removed splitting by N.NBR

P.opt <- data.frame(Reduce(rbind,lapply(test, get.p))) 
P.opt <- P.opt %>% mutate(p.RMV = as.vector(sapply(test, function(x) x$p.RMV[1])),
         p.SST = as.vector(sapply(test, function(x) x$p.SST[1]))) %>%
         mutate(p.SST.f = factor(p.SST))

names(P.opt) <- c("intercept", "slope.b1", "slope.b2", "p.opt",  
                  "p.RMV", "p.SST", "p.SST.f")
P.opt <- P.opt %>% filter(!is.na(p.opt))

Fitted$p[[r]] <- P.opt
```

Plot:

```{r}
p1 <- ggplot(Res.p %>% mutate(p.SST=p.SST.f), 
             aes(x=p, y=CP.within.fruit, color=p.SST)) +
  geom_point() + geom_hline(yintercept = Estimate) + theme_bw() +
  geom_smooth(method="lm", se=FALSE, formula=y ~ x + I(x^2))
```

Express p as a function of p.SST:

```{r fig.height=3, fig.width=8}
tmp<- rbind(P.opt, c(NA, NA, NA, Fitted$p.fit[r,"fit"], NA, 0, NA))
p2 <- ggplot(tmp , aes(x=p.SST, y=p.opt)) + 
  geom_point(color=c(rep("black", nrow(P.opt)), "violetred2")) +
  stat_smooth(data=P.opt %>% filter(p.SST >= 0.1), method="lm", se=FALSE, 
              formula=y ~ x + I(x^2)) 

g1 <- gridExtra::grid.arrange(p1, p2, nrow = 1)
grid::grid.draw(g1)
```

Export figures:

```{r}
pdf(paste0(here::here(), "/Fit_p.opt.pdf"), width=8, height=3)
grid::grid.draw(g1)
dev.off()
```

```{r}
Models=list( mod1=lm(p.opt ~ p.SST , 
                       data=P.opt %>% filter(p.SST >= 0.1)),
             mod3=lm(p.opt ~ p.SST + p.SST.2, 
                       data=P.opt %>% filter(p.SST >= 0.1) %>% 
                       mutate(p.SST.2 = p.SST^2)))

a <- order(sapply(Models, AIC))[1]
best <- Models[a][[1]]
summary(best) 

P.opt$p.smooth[P.opt$p.SST >= 0.1] <- fitted(best)

Fitted$p[[r]] <- P.opt
Fitted$Smoothing[[r]] <- list()
Fitted$Smoothing[[r]]$p <- best
```

### Step 3: Expressing N.NBR as a function of p.SST

#### Model CP between moms 

Model CP between moms as a function of `p.SST` (and associated values of `p` and `p.RMV`) and `N.NBR` to express `N.NBR` as a function of `p.SST`.

```{r}
X <- expand.grid(p.SST=Fitted$p[[r]] %>% pull(p.SST),
            N.NBR=c(3,5,6,7,8,9,12,18,25))
X <- left_join(X, Fitted$p[[r]] %>% mutate(p=p.smooth) %>% select(p.SST, p.RMV, p))
X <- X %>% filter(!is.na(p))

R <- 10
X <- X[rep(1:nrow(X),R),]

Res <- data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                       fx(y=X$p.SST[i], z=X$p.RMV[i], w=X$N.NBR[i], p=X$p[1]), 
                          mc.cores=parallel::detectCores())))

Res.N.NBR <- Res %>% mutate(p.SST.f=factor(p.SST))
saveRDS(Res.N.NBR, paste0(here::here(), "/Res.N.NBR.rds"))
#Res.N.NBR <- readRDS(paste0(here::here(), "/Res.N.NBR.rds"))

Estimate <- Rates.table["Between Moms Outcrossed", r]
```

```{r}
p1 <- ggplot(data = Res.N.NBR , aes(x = N.NBR, y = CP.between.mom, col = p.SST.f)) +
  geom_point(size=0.8) + 
  scale_x_continuous(trans='log', breaks=c(3,5,6,7,8,9,12,18,25), 
                          minor_breaks=NULL) +
  scale_y_continuous(trans='log', breaks=c(0.002, 0.005, 0.01, 0.02), 
                           minor_breaks=NULL) +
  geom_smooth(method=lm, se=FALSE, size=0.8) + theme_bw() +
  geom_hline(yintercept=Estimate) 
  
p1
```

Fit separate intercepts and slopes:

```{r}
mod.lm <- lm(log(CP.between.mom) ~ log(N.NBR) * p.SST.f, data=Res.N.NBR)
n=nlevels(Res.N.NBR$p.SST.f)
intercept <- mod.lm$coefficients[c(1:(n+1))[-2]]
intercept[-1] <- intercept[-1] + intercept[1]
slope <- mod.lm$coefficients[c(2, c(2:n) + n)]
slope[-1] <- slope[-1] + slope[1]

df <- data.frame(p.SST.f=levels(Res.N.NBR$p.SST.f), intercept=intercept, slope=slope)
df <- df %>% mutate(N.NBR.opt = exp((log(Estimate) - intercept) / slope),
                    p.SST=as.numeric(p.SST.f)) %>%
             mutate(p.SST.2 = p.SST^2)
```

Express `N.NBR` as a function of `p.SST`.

```{r}
mod2 <- lm(N.NBR.opt ~ p.SST + p.SST.2, data=df)
summary(mod2)

df$smooth <- predict(mod2, df)
df$N.NBR.fit <- round(df$smooth)

Fitted$N.NBR[[r]] <- df
#Fitted$Smoothing[[r]] <- list()
Fitted$Smoothing[[r]]$N.NBR <- mod2

```

```{r fig.height=3, fig.width=8}
p2 <- ggplot(data = df, aes(x = p.SST, y = N.NBR.opt)) +
  geom_point() + 
  geom_smooth(method="lm", se=FALSE, formula='y ~ x + I(x^2)') 

g1 <- gridExtra::grid.arrange(p1, p2, nrow = 1, widths=c(0.57, 0.43))
grid::grid.draw(g1)
```

Export figures:

```{r}
pdf(paste0(here::here(), "/Fit_N.NBR.opt.pdf"), width=8, height=3)
grid::grid.draw(g1)
dev.off()
```

### Step 4: Optimizing p.SST

#### Model CP between fruits 

Model CP between fruits as a function of p.SST (and the associated values of p, p.RMV and N.NBR): what rate of sample-and-shift behaviour would result in the observed CP between fruits?

```{r}
#r = 2  # Select set of rates

X <- Fitted$N.NBR[[r]] %>% mutate(N.NBR=N.NBR.fit) %>% 
                           select(p.SST, p.SST.2, N.NBR)
X <- X %>% mutate(p=predict(Fitted$Smoothing[[r]]$p, newdata=X))
X <- X %>% mutate(p.RMV=Rates.table["Local Mating Outcrossed",r]/(p * p.SST))

R <- 30
X <- X[rep(1:nrow(X),R),]

Res <-data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                       fx(y= X$p.SST[i], z=X$p.RMV[i], w=X$N.NBR[i], p=X$p[i]), 
                          mc.cores=parallel::detectCores())))

Res.p.SST <- Res
saveRDS(Res.p.SST, paste0(here::here(), "/Res.p.SST.rds"))
#Res.p.SST <- readRDS(paste0(here::here(), "/Res.p.SST.rds"))

Estimate <- Rates.table["Between Fruit Outcrossed", r]
```

```{r}
Dat <- Res.p.SST %>% group_by(p.SST) %>% 
  summarize(CP.between.fruit=mean(CP.between.fruit))

ggplot(Dat, aes(x=p.SST, y=CP.between.fruit)) + geom_point() + 
    geom_hline(yintercept=Estimate) +
    stat_smooth(method="glm", se=F, formula='y ~ x', 
                method.args = list(family="gaussian"(link=log)))

ggsave("Fit_p.SST.pdf", width = 5, height = 3.5, units = "in")
```

```{r}
mod.glm <- glm(CP.between.fruit ~ p.SST, data=Res.p.SST, family=gaussian(link="log"))
summary(mod.glm)
   
p.SST.opt <- as.vector((log(Estimate) -mod.glm$coef[1]) / mod.glm$coef[2])

P.SST.opt <- data.frame(p.SST=p.SST.opt) %>% mutate(p.SST.2=p.SST^2)
P.SST.opt <- P.SST.opt %>% 
  mutate(p=predict(Fitted$Smoothing[[r]]$p, newdata=P.SST.opt)) %>%
  mutate(p.RMV=Rates.table["Local Mating Outcrossed",r]/(p * p.SST)) %>%
  mutate(N.NBR = predict(Fitted$Smoothing[[r]]$N.NBR, newdata=P.SST.opt))

P.SST.opt <- P.SST.opt %>% select(-p.SST.2) %>% 
  mutate(N.NBR.smooth=N.NBR) %>%
  mutate(N.NBR=round(N.NBR))
Fitted$p.SST[[r]] <- P.SST.opt 
Fitted$Smoothing[[r]]$p.SST <- mod.glm

#saveRDS(Fitted, paste0(here::here(), "/Fitted.rds"))
```

## 3. Pattern-oriented simulation modeling for territorial foraging

### Fit pTF to CP.between.fruit

```{r}
r = 2  # Select set of observed rates
gc() # garbage collection - avoid errors

X <- expand.grid(p=Fitted$p.fit$fit[r], 
                     p.TF=sort(unique(c(seq(0.05,0.5,0.05)))),
                     N.NBR=c(4,6,8,10))

X <- X %>% mutate(p2=p) 

R <- 30
X <- X[rep(1:nrow(X),R),]
Res <- data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                       fx(u=X$p.TF[i], v=X$p2[i], w=X$N.NBR[i], p=X$p[i]), 
                          mc.cores=parallel::detectCores())))

Res.p.TF <- Res
saveRDS(Res.p.TF, paste0(here::here(), "/Res.p.TF.rds"))
#Res.p.TF <- readRDS(paste0(here::here(), "/Res.p.TF.rds"))
```

```{r}
Estimate <- Rates.table["Between Fruit Outcrossed", r]

Dat.p.TF <- Res.p.TF %>% group_by(p.TF, N.NBR) %>% 
  summarize(CP.between.fruit=mean(CP.between.fruit),
            CP.between.mom=mean(CP.between.mom),
            Local=mean(Local))

plot1 <- ggplot(Dat.p.TF %>% mutate(N.NBR=factor(N.NBR)), 
       aes(p.TF, CP.between.fruit, group=N.NBR, col=N.NBR)) +
  geom_point() + ylim(0, 0.2) +
  stat_smooth(method="lm", se=F, formula='y ~ x + I(x^2)') +
  geom_hline(yintercept=Estimate) + 
  geom_segment(x=0.25, y=0, xend=0.25, yend=Estimate, 
               linetype = "dashed", col="darkgray", size=0.7) 
plot1 + theme_light()
```

Optimize/smooth p.TF as a function of N.NBR (to fit CP.between.fruit).

```{r}
r=2
Estimate <- Rates.table["Between Fruit Outcrossed", r]

optimize.p.TF <- function(x, E, a, b1, b2)
{
  (E - (a + b1 * x + b2 * I(x^2)))^2
}

get.p.TF <- function(ls)
{
  # Version date: March 13, 2022
  
  #mod1 <- lm(CP.between.fruit ~ p2, data=ls)
  mod1 <- lm(CP.between.fruit ~ p.TF + I(p.TF^2), data=ls)
  p.TF.opt <- NA
  if(sum(is.na(mod1$coef)) == 0)
  {
    p.TF.opt <- optimize(optimize.p.TF, interval=c(0.01, 1), 
                    E=Estimate, a=mod1$coef[1], b1=mod1$coef[2],
                    b2=mod1$coef[3])$minimum
  }
  
  c(a=mod1$coef[1], b1=mod1$coef[2], p.TF.opt=p.TF.opt)
}

# Limit to range that has sufficient data and results in positive values of p.TF.
tmp <- Res.p.TF %>% mutate(N.NBR = factor(N.NBR))
test <- split(tmp, tmp$N.NBR)
P.TF.opt <- data.frame(Reduce(rbind,lapply(test, get.p.TF)))

P.TF.opt$N.NBR <- as.numeric(names(test))
names(P.TF.opt)[1:2] <- c("Intercept", "slope")
rownames(P.TF.opt) <- NULL
P.TF.opt
```

### Plot against CP.between.mom and Local mating 

Note: models were only fitted with ggplot, not numerically, as there was no fit consistent with all mating system parameters.

```{r fig.height=3, fig.width=6}
r=2
Estimate <- Rates.table["Between Moms Outcrossed", r]

# Linear model
plot2 <- ggplot(Dat.p.TF %>% mutate(N.NBR=as.factor(N.NBR)), 
         aes(x=p.TF, y=CP.between.mom, group=N.NBR, color=N.NBR)) +
  geom_smooth(method="lm", se=FALSE, formula='y ~ x + I(x^2)') + geom_point() +
  geom_hline(yintercept = Estimate) +
  geom_vline(xintercept = 0.25, linetype = "dashed", 
             col="darkgray", size=0.7) 
plot2 + theme_light()
```

```{r fig.height=3, fig.width=6}
r=2
Estimate <- Rates.table["Local Mating Outcrossed", r]

# Linear model
plot3 <- ggplot(Dat.p.TF %>% mutate(N.NBR=as.factor(N.NBR)), 
         aes(x=p.TF, y=Local, group=N.NBR, color=N.NBR)) +
  geom_smooth(method="lm", se=FALSE, formula='y ~ x') + geom_point() +
  geom_hline(yintercept = Estimate) + ylim(-0.01,0.4) +
  geom_vline(xintercept = 0.25, linetype = "dashed", 
             col="darkgray", size=0.7) 
plot3 + theme_light()
```

```{r}
gTF <- cowplot::plot_grid(plot1 + theme_light(), plot2 + theme_light(), 
                          plot3 + theme_light(), align = "v", ncol = 1)
ggsave(file="Fitting.TF.pdf", plot=gTF, width=6, height = 7)
gTF
```

## 4. Simulate mating system parameters with the inferred parameter values

Scenarios:

- Complete traplining.
- Inferred tactic of SST.
- Inferred rate of territorial foraging (0.25) (not included in manuscript).
- Territorial foraging only.

```{r}
r=2
X <- Fitted$p.SST[[r]] %>% select(-N.NBR.smooth)
X[2,] <- c(0,get.p.fit.within(Rates.table["Within Fruit Outcrossed",r]), 1, X[1,4])
X$p2 = NA
X$p.TF=0

X[3,] <- c(0, get.p.fit.within(Rates.table["Within Fruit Outcrossed",r]), 1, X[1,4],
           get.p.fit.within(Rates.table["Within Fruit Outcrossed",r]), 0.25)
X[4,] <- c(0, get.p.fit.within(Rates.table["Within Fruit Outcrossed",r]), 1, X[1,4],
           get.p.fit.within(Rates.table["Within Fruit Outcrossed",r]), 1)

R <- 100
X <- X[rep(1:nrow(X),R),]

Res <- data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                       fx.site(y=X$p.SST[i], z=X$p.RMV[i], w=X$N.NBR[i], p=X$p[1],
                          u=X$p.TF[i], v=X$p2[i]), 
                          mc.cores=parallel::detectCores())))
Res.final <- Res
```

```{r}
Set.Table <- Res.final %>% 
  group_by(p.SST, p.RMV, p.TF, p, N.NBR) %>%
  summarize(CP.within.fruit.mean=mean(CP.within.fruit), 
            CP.within.fruit.s=sd(CP.within.fruit),
            CP.between.fruit.mean=mean(CP.between.fruit), 
            CP.between.fruit.s=sd(CP.between.fruit),
            CP.within.mom.mean=mean(CP.within.mom), 
            CP.within.mom.s=sd(CP.within.mom),
            CP.between.mom.mean=mean(CP.between.mom), 
            CP.between.mom.s=sd(CP.between.mom),
            Local.mating.mean=mean(Local), 
            Local.mating.s=sd(Local),
            Nep.mean=mean(Nep), 
            Nep.s=sd(Nep),
            Nep.site.mean=mean(Nep.site),
            Nep.site.s=sd(Nep.site))

#View(Set.Table)

write.table(format(as.data.frame(Set.Table), digits=3), 
            paste0(here::here(), "/Set.Table.txt"), sep="\t", row.names=FALSE, quote=FALSE)

#Fitted$Set.Table <- list()
Fitted$Set.Table[[r]] <- Set.Table
saveRDS(Fitted, paste0(here::here(), "/Fitted.rds"))
```

## 5. Sensitivity analysis for complete vs. sample-and-shift trapling foraging

Simulate pollen loads for a broad range of trapline foraging parameter values to assess their effect on mating system parameters. 

```{r}
r = 2  # Select set of rates

X <- expand.grid(p.SST = c(0, 0.131, 0.5, 1),
                 N.NBR = c(6, 20),
                 p.RMV = c(0, 0.056, 0.1, 0.2, 0.5, 1),
                 p=c(0.2, 0.366, 0.5, 1))
R <- 5
X <- X[rep(1:nrow(X),R),]
X.f <- X %>% mutate(p.SST.f = factor(p.SST), p.RMV.f=factor(p.RMV),
                                   N.NBR.f=factor(N.NBR), p.f=factor(p))

Res <-data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                    fx(y=X$p.SST[i], z= X$p.RMV[i], w=X$N.NBR[i], p=X$p[i]),
                    mc.cores=parallel::detectCores())))

Sensitivity <- list(X=X, X.f=X.f, Res=Res)

saveRDS(Sensitivity, paste0(here::here(), "/Sensitivity.rds"))
#Sensitivity <- readRDS(paste0(here::here(), "/Sensitivity.rds"))
```

Interaction plots: assemble data.

```{r message=FALSE}
Dat <- Sensitivity$Res %>% 
  mutate(N.NBR = factor(N.NBR), 
         p.SST = factor(p.SST), p=factor(p, levels=c(1, 0.5, 0.366, 0.2))) %>% 
  group_by(p.SST, p.RMV, N.NBR, p) %>% 
  summarise(Nep = mean(Nep), Local.mating=mean(Local))
```

Plot Nep:

```{r fig.height=4, fig.width=8}
p1 <- ggplot(Dat,  aes(p.RMV, Nep)) +
  geom_line(size = 1, aes(group = p.SST, color = p.SST)) +
  geom_point(size = 2, aes(color = p.SST), shape = 16) +
  geom_point(data=Dat %>% filter(p.SST==0.131, N.NBR==6, p.RMV==0.056, p==0.366),
             size = 2.5, shape = 17, color="violetred2") +
  facet_grid(N.NBR ~ p, labeller = label_both) + theme_bw() +
  scale_y_continuous(trans='log', breaks=c(1, 10, 100, 1000)) +
  scale_x_continuous(breaks=c(0, 0.2,0.5, 1), minor_breaks = c(0.056, 0.1,0.2)) +
  ggthemes::scale_colour_colorblind()

ggsave(file="Nep.pdf", plot=p1, width=8, height = 4)
p1
```

Plot local mating:

```{r fig.height=4, fig.width=8}
p2 <- ggplot(Dat, aes(p.RMV, Local.mating)) +
  geom_line(size = 1, aes(group = p.SST, color = p.SST)) +
  geom_point(size = 2, aes(color = p.SST), shape = 16) +
  geom_point(data=Dat %>% filter(p.SST==0.131, N.NBR==6, p.RMV==0.056, p==0.366),
             size = 2.5, shape = 17, color="violetred2") +
  scale_x_continuous(breaks=c(0, 0.2, 0.5, 1), minor_breaks = c(0.056, 0.1)) +
  scale_y_continuous(breaks=c(0, 0.25, 0.5, 0.75, 1), minor_breaks = NULL) +
  facet_grid(N.NBR ~ p, labeller = label_both) + theme_bw() +
  ggthemes::scale_colour_colorblind()

ggsave(file="Local.mating.pdf", plot=p2, width=8, height = 2.2)
p2
```

## 6. Sensitivity analysis for territorial foraging

```{r}
r = 2  # Select set of rates

X <- expand.grid(p.TF = c(0, 0.25, 0.5, 1),
                 N.NBR = c(6, 20),
                 p.RMV = c(0),
                 p=c(0.2, 0.366, 0.5, 1))
R <- 30
X <- X[rep(1:nrow(X),R),]
X.f <- X %>% mutate(p.TF.f = factor(p.TF),
                    N.NBR.f=factor(N.NBR), p.f=factor(p))

Res.TF <-data.frame(X, Reduce(rbind, pbmcapply::pbmclapply(1:nrow(X), function(i) 
                    fx(y=0, z=1, w=X$N.NBR[i], p=X$p[i], u=X$p.TF[i], v= X$p[i]),
                    mc.cores=parallel::detectCores())))

Sensitivity.TF <- list(X=X, X.f=X.f, Res=Res.TF)

saveRDS(Sensitivity.TF, paste0(here::here(), "/Sensitivity.TF.rds"))
#Sensitivity.TF <- readRDS(paste0(here::here(), "/Sensitivity.TF.rds"))
```

Assemble data for plots:

```{r}
Dat.TF <- Sensitivity.TF$Res %>% 
  mutate(N.NBR = factor(N.NBR), p.TF = factor(p.TF)) %>% 
  group_by(p.TF, N.NBR, p) %>% 
  summarise(Nep = mean(Nep), Local.mating=mean(Local))
```

```{r fig.height=2, fig.width=2.5}
p1.TF <- ggplot(Dat.TF,  aes(p, Nep)) +
  geom_line(size = 1, aes(group = p.TF, color = p.TF)) +
  geom_point(size = 2, aes(group = p.TF, color = p.TF)) +
  facet_grid(rows=vars(N.NBR) , labeller = label_both) + theme_bw() +
  scale_y_continuous(trans='log', breaks=c(1, 10, 100, 1000), limits=c(1,1000)) + 
  scale_x_continuous(breaks=c(0.2, 0.366, 0.5, 1), minor_breaks = NULL) +
  ggthemes::scale_colour_colorblind()
p1.TF 
```

```{r fig.height=2, fig.width=3}
p2.TF <- ggplot(Dat.TF,  aes(p, Local.mating)) +
  geom_line(size = 1, aes(group = p.TF, color = p.TF)) +
  geom_point(size = 2, aes(group = p.TF, color = p.TF)) +
  facet_grid(rows=vars(N.NBR), labeller = label_both) + theme_bw() +
  scale_y_continuous(breaks=c(0, 0.25, 0.5, 0.75, 1), minor_breaks = NULL,
                     limits=c(0,1)) +
  scale_x_continuous(breaks=c(0.2, 0.366, 0.5, 1), minor_breaks = NULL) +
  ggthemes::scale_colour_colorblind()
p2.TF
```

```{r}
g1 <- cowplot::plot_grid(p1.TF, p2.TF,
                         align = "v", ncol = 2)
ggsave(file="Sensitivity.TF.pdf", plot=g1, width=8, height = 2.5)
g1
```